### 2021-04-02 Chapter-3/Chapter-3.tex
update

\section{Method}
\begin{figure}
    \centering
    \includegraphics[width=.35\columnwidth]{./figures/chapter3/attack.pdf}
    \caption{A side-channel attack}\label{fig:side-channel-attack}
\end{figure}

In the section, we give necessary definitions and notation for dealing with
programs and side-channels.

Shown in Figure~\ref{fig:side-channel-attack}. We assume a program ($\beta$) has $K$ as its sensitive input.  The program also takes public information $M$ as its input. During an AES encryption, for example, 
$\beta$ is the encryption function. $K$ is the set of all possible AES keys, 
and $M$ represents the set consisting of all plaintext messages to be encrypted. In a real execution, an adversary may have 
some observations ($O$) of the program. Examples of those observations include 
timing, CPU usages, and electromagnetic signals (EM). This paper only
uses secret-dependent control flows and secret-dependent data 
accesses as observations.

With the above definition, we have the following mapping between $\beta$,
$K$, $M$, and $O$:
%\vspace*{-0pt}
\begin{displaymath}
    \beta(K, M) \rightarrow O
\end{displaymath}

We model a side-channel in the following way. An adversary does not have
access to $K$, but he knows $\beta$, $M$, and $O$. For one execution of a
deterministic program, once $k \in K$ and $m \in M$ are fixed, the observation
($o \in O$) should also be determined. An attacker knows $\beta$, $o$,
and $m$. The attacker wants to infer the value of $k$. We use $K^o$ to denote
the set of possible $k$ values that produce the same observation: $K^o = \{ k \in K \, |\, \beta(k, m) \rightarrow o\}$

We now discuss how to model observations ($O$), which are the direct information that an adversary can get during the attack.

During the execution, a program ($\beta$) have many temporary values ($t_i \in
T$). Once $\beta$ (program), $k$ (secret), and $m$ (message, public) are
determined, $t_i$ is also fixed. Therefore, $ t_i = f_i(\beta, k, m)$, where $f_
i$ is a function that maps between $t_i$ and ($\beta$, $k$, $m$).

In the paper, we consider two code patterns that can be exploited by an attacker,
\emph{secret-dependent control transfers} and \emph{secret-dependent data
accesses}. In other words, an adversary has observations based on control-flows
and data accesses.

\subsection{Secret-dependent Control Transfers}
We think a control-flow is secret-dependent if different input sensitive keys
($K$) can lead to different branch conditions. Therefore,
We define a branch is secret-dependent if:
$$\exists k_{i1}, k_{i2} \in K , \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m)$$

>>>>

\section{Method}
\begin{figure}
    \centering
    \includegraphics[width=.3\columnwidth]{./figures/chapter3/attack.pdf}
    \caption{A side-channel attack}\label{fig:side-channel-attack}
\end{figure}

In the section, we give necessary definitions and notations for dealing with
programs and side-channels.

Shown in Figure~\ref{fig:side-channel-attack}, a side-channel attack can be formulated into the below steps.  A program ($\beta$) has $K$ as its sensitive input (e.g., the encryption key) and $M$ as its the public input (e.g., the plaintext). In a real execution, an adversary may have 
some observations ($O$) of the program. Examples of those observations include the
timing, CPU usages, and electromagnetic signals (EM). In this dissertation, we 
use secret-dependent control flows and secret-dependent data 
accesses as observations.

With the above definition, we have the following mapping between $\beta$,
$K$, $M$, and $O$:
\begin{displaymath}
    \beta(K, M) \rightarrow O
\end{displaymath}

We model a side-channel in the following way. An adversary does not have
access to $K$, but he knows $\beta$, $M$, and $O$. For one execution of a
deterministic program, once $k \in K$ and $m \in M$ are fixed, the observation
($o \in O$) should also be determined. An attacker knows $\beta$, $o$,
and $m$. The attacker wants to infer the value of $k$. Moreover, we assume
an attacker can change the public input ($m \in M$) while keeping the secret input $k$. 
The threat model is similar to a chosen-plaintext attack.
We now discuss how to model observations ($O$), 
which are the direct information that an adversary can get during the attack.

For one execution, a program ($\beta$) has many temporary values ($t_i \in
T$). Once $\beta$ (program), $k$ (secret), and $m$ (message, public) are
determined, $t_i$ is also fixed. Therefore, $ t_i = f_i(\beta, k, m)$, where $f_
i$ is a function that maps between $t_i$ and ($\beta$, $k$, $m$). In the paper, 
we consider two code patterns that can be exploited by an attacker,
\emph{secret-dependent control transfers} and \emph{secret-dependent data
accesses}. In other words, an adversary has observations based on control-flows
and data accesses.

\subsection{Secret-dependent Control Transfers}
We think a control-flow is secret-dependent if different input sensitive keys
($K$) can lead to different branch conditions. Therefore,
We define a branch is secret-dependent if:
$$\exists k_{i1}, k_{i2} \in K, m \in M, \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m)$$
